\bf Model Visualization Techniques for a Social Network Model

### 2017-09-15 paper.Rnw
match all adjacency matrices (x,y)

p1 <- ggplot(data = numordersf, aes(x = from, y = to)) + geom_tile(color = 'black', aes(fill = as.factor(value))) + 
  scale_fill_manual(values = c('white', 'black')) +
  scale_x_discrete(position = "top", labels = as.character(1:16)) +
  scale_y_discrete(labels = rev(as.character(1:16)))  + 
  ThemeNoNet + 
  theme(legend.position = 'none') + 
  coord_fixed()

@@

<<adjmatani, fig.cap='A selection of frames from the adjacency matrix visualization animation for one series of microsteps. At the beginning of the animation, shown in the top row, there are two clearly connected components: one in the top left corner, and one in the bottom right corner. By the end, the component in the top left has spread out, while the bottom right component has shrunk, but remains closely connected.', fig.show='animate', warning = FALSE, message = FALSE, interval=.2, results='hide', fig.height=4>>=
adjmatall <- matrix(0, nrow = 16, ncol = 16)
rownames(adjmatall) <- paste0("V", 1:16)
colnames(adjmatall) <- paste0("V", 1:16)
dat2 <- sfmsall %>% filter(rep == 1)
adjmatall2 <- NULL
for(i in 0:55){
  MS <- dat2[dat2$ms == i,c("from", "to")]
  myadjmat <- adjmatall
  for(j in 1:nrow(MS)){
    myadjmat[MS[j,"from"][[1]],MS[j,"to"][[1]]] <- 1
  }
  adjmatall2 <- rbind(adjmatall2, myadjmat)
}

>>>>

p1 <- ggplot(data = numordersf, aes(y = from, x = to)) + geom_tile(color = 'black', aes(fill = as.factor(value))) + 
  scale_fill_manual(values = c('white', 'black')) +
  scale_x_discrete(position = "top", labels = as.character(1:16)) +
  scale_y_discrete(labels = rev(as.character(1:16)))  + 
  ThemeNoNet + 
  theme(legend.position = 'none') + 
  coord_fixed()

@@

<<adjmatani, fig.cap='A selection of frames from the adjacency matrix visualization animation for one series of microsteps. At the beginning of the animation, shown in the top row, there are two clearly connected components: one in the top left corner, and one in the bottom right corner. By the end, the component in the top left has spread out, while the bottom right component has shrunk, but remains closely connected.', warning = FALSE, message = FALSE, results='hide', fig.height=4>>=
adjmatall <- matrix(0, nrow = 16, ncol = 16)
rownames(adjmatall) <- paste0("V", 1:16)
colnames(adjmatall) <- paste0("V", 1:16)
dat2 <- sfmsall %>% filter(rep == 1)
adjmatall2 <- NULL
for(i in 0:55){
  MS <- dat2[dat2$ms == i,c("from", "to")]
  myadjmat <- adjmatall
  for(j in 1:nrow(MS)){
    myadjmat[MS[j,"from"][[1]],MS[j,"to"][[1]]] <- 1
  }
  adjmatall2 <- rbind(adjmatall2, myadjmat)
}
